\sysfull

### 2017-07-28 paper/evaluation.tex
bibs have proper links

In the experiments we used WISP\,5.1~\cite{wisp5,wisp} (with MSP430FR5969~\cite{wolverine} 64\,kB FRAM) or MSP430XXX launchpad~\cite{} (hardware type will be specified per experiment in Section~\ref{sec:results_evaluation}). WISP\,5.1 has been programmed using TI FET for experiments. FET was also used as a power supply in non-intermittent power experiment. To measure energy consumption of the applications (refer to Section~\ref{sec:results_software}) EDB~\cite{edb} was used. In experiments involving wireless power, WISP was powered through RFID reader (Impinj R1000 with firmware version 3.2.4.240~\cite{r1000_data_sheet}) connected to Liard RFMAX S9028PCRJ 8\,dBic~\cite{atlas2015}. RFID reader is controlled by a PC running Ubuntu 10.4 executing open source Python-based \emph{sllurp} library~\cite{sllrp_github} enabling low-level RFID reader control. Transmitted power of the RFID reader was 30\,dBm at 915\,MHz center frequency. For distance controlled experiments, WISP was positioned at hollow paper tubes placed directly on a lying antenna.

>>>>

In all experiments we used the following computing hardware: WISP\,5.1~\cite{wisp5,wisp}, i.e. build around MSP430FR5969~\cite{wolverine} 64\,kB FRAM microcontroller, and TI's MSP430FR5969 launchpad~\cite{MSP-EXP430FR5969_launchpad} (hardware type will be specified per experiment in Section~\ref{sec:results_evaluation}). WISP\,5.1 has been re-programmed during experiments using TI's Flash Emulation Tool (FET)~\cite{fet}. FET was also used as a power supply in non-intermittent power experiment. To measure energy consumption of all benchmark applications (please refer to Section~\ref{sec:results_software}) Carnegie Mellon's EDB~\cite{edb} was used. In experiments involving wireless power, WISP was powered through an RFID reader (Impinj R1000 with firmware version 3.2.4.240~\cite{r1000_data_sheet}) connected to Liard RFMAX S9028PCRJ 8\,dBic~\cite{atlas2015}. RFID reader is controlled by a PC running Ubuntu 10.4 executing open source Python-based \emph{sllurp} library~\cite{sllrp_github} enabling low-level RFID reader control. Transmitted power of the RFID reader was 30\,dBm at 915\,MHz center frequency. For distance controlled experiments, WISP was positioned at varying length hollow paper tubes placed directly on a flat lying antenna. Code completion measurements have been performed using Salea~\cite{saleae} digital logic analyzer.
